Predicting Fire Risk: \\ An Evaluation of the Fire Danger Index

### 2016-05-13 paper.tex
map changed
update figures, and appendix

\begin{figure}
  \centering
  \includegraphics[width=.7\textwidth]{figures/cfadis.pdf}
  \caption{Country Fire Authority Districts}
  \label{fig:dist}
\end{figure}

\todo[inline]{Change Figure \ref{fig:dist} to have statistical divisions}

%Commented out until final printing,
%Map of fire ignitions in Victoria
\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{figures/firemap.pdf}
  \caption{Map of fire ignition 2000 - 2009}
  \label{fig:firemap}
\end{figure}

%timeseries histogram with count of ignitions per fortnight
\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{figures/occurence.pdf}
  \caption{Number of ignitions by fortnight}
  \label{fig:occ}
\end{figure}

@@

As classification trees can be sensitive to the sample used, we constructed several trees on different balanced samples of the data. As each of the trees were structured very similarly we only report two in Figure~\ref{fig:tree2}.

For both the reported trees, curing is the first and second split on the tree. When the same variable is used for consecutive splits in a classification tree there are bands of values which the variable takes which are determining the outcome.

@@

The variable importance is calculated as mean decrease in accuracy using the out-of-bag observations, described in detail by \citet{archer08}. Figure~\ref{fig:vimp} shows the variable importance for the forest.

@@

Similar variable importance may indicate that on the average across all trees the variables are equally important in determining probability of ignition, however variable importance cannot necessarily be taken simply at face value. \citet{strob07}  and \citet{strob08} show that variable importance measures may be biased by the measurement scale of the variables and show a preference for correlated variables. Alternative calculation of variable importance is outside the scope of this paper but the limitations of the Gini method should be taken into account.

Table~\ref{table:correl} is the cross-correlation matrix for the variables and we observe that many of the variables have relatively high correlation coefficients (with the exception of vapour pressure and windspeed) which may be causing biased variable importance.

@@

>>>>

%\begin{figure}
%  \centering
%  \includegraphics[width=.7\textwidth]{figures/cfadis.pdf}
%  \caption{Country Fire Authority Districts}
%  \label{fig:dist}
%\end{figure}

%Commented out until final printing,
%Map of fire ignitions in Victoria
\begin{figure}
  \centering
  \includegraphics[width=.95\textwidth]{figures/firemap.pdf}
  \caption{Map of fire ignition 2000 - 2009, and districts. Locations of fires are similar from year to year, so they have been combined into one map. The higest density is around the city, and straight lines would suggest along roads. We cannot say that the locations are due to fires being started in, or if they are recorded at, convenient locations.}
  \label{fig:firemap}
\end{figure}

%timeseries histogram with count of ignitions per fortnight
\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{figures/occurence.pdf}
  \caption{Number of ignitions in each fortnight over 2000-2010. The earlier years saw more fires, particularly 2001. Only fires during fire season were analysed.}
  \label{fig:occ}
\end{figure}

@@

As classification trees can be sensitive to the sample used, we constructed several trees on different balanced samples of the data. 
For the trees, curing is the first and second split on the tree. When the same variable is used for consecutive splits in a classification tree there are bands of values which the variable takes which are determining the outcome.

@@

The variable importance is calculated as mean decrease in accuracy using the out-of-bag observations, described in detail by \citet{archer08}.

@@

Similar variable importance may indicate that on the average across all trees the variables are equally important in determining probability of ignition, however variable importance cannot necessarily be taken simply at face value. \citet{strob07}  and \citet{strob08} show that variable importance measures may be biased by the measurement scale of the variables and show a preference for correlated variables. Alternative calculation of variable importance is outside the scope of this paper but the limitations of the Gini method should be taken into account.
%Table~\ref{table:correl} is the cross-correlation matrix for the variables and 
We observed that many of the variables have relatively high correlation coefficients (with the exception of vapour pressure and windspeed) which may be causing biased variable importance.

@@

As each of the trees were structured very similarly we only report two in Figure~\ref{fig:tree2}.

Figure~\ref{fig:vimp} shows the variable importance for the forest.
